State of the Art in \\ {\ttlit Twitter Sentiment Analysis}

### 2015-01-21 paper/chapters/4_classification.tex
paper

\section{Classification}
Insert general classification information here.

\begin{enumerate}
\item Supervised vs. unsupervised
\item Training Set
\end{enumerate}

\subsection{Machine Learning Algorithms}
According to the paper by Qiang et al.\autocite{Ye20096527} the most important approaches in 
text mining and sentiment classification are Naive Bayes, SVM and 
N-gram.

@@

\subsubsection{Support vector machines for sentiment classification}

@@

>>>>

\section{Classification}
Based on the preprocessed data a machine learning algorithm can be applied which aims to classify the polarity of the given input data. [...]

%Ideen:
%\begin{enumerate}
%\item Supervised vs. unsupervised
%\item Training Set
%\item FeatureVector
%\item N-Grams
%\end{enumerate}
%

\subsection{Machine Learning Algorithms}
According to the paper by Qiang et al.\autocite{Ye20096527} the most important approaches in 
text mining and sentiment classification are Naive Bayes, Support Vector Machines and 
N-gram. Maximum Entropy Classification is also often mentioned by various papers regarding 
classification in sentiment analysis.

@@

\subsubsection{Support Vector Machines for sentiment classification}

@@

\subsubsection{Maximum Entropy classification}
